Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-08-18 longSC.tex

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/chisq_bestfits_3pad.eps}}
        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for SC($m$,$n$) (a),  NSC($m$,$n$) (b) and individual harmonics $v_n$ (c).}
        %The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
        \label{fig:Figure_A5}
              \end{center}
\end{figure*}

>>>>

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.99\textwidth}{!}{\includegraphics{figs/chisq_bestfits_3pad.eps}}
        \caption{The ${\chi}^2$ values from the comparison of few selected calculations from three theoretical models are shown for SC($m$,$n$) (a),  NSC($m$,$n$) (b) and individual harmonics $v_n$ (c). The ${\chi}^2$ results for SC($m$,$n$) (NSC($m$,$n$)) are shown as closed (open) markers.}
        \label{fig:Figure_A5}
              \end{center}
\end{figure*}
